Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-01-19 paper/aldebaran.tex
Added Julia to software stack in ack's.

\software{\textsc{IPython} \citep{PER-GRA:2007}, SciPy \citep{scipy}, \textsc{matplotlib} \citep{Hunter:2007}, \textsc{Astropy} \citep{2013A&A...558A..33A}, \textsc{NumPy} \citep{van2011numpy}, \textsc{isochrones} \citep{isochrones}.}

>>>>

\software{\textsc{IPython} \citep{PER-GRA:2007}, SciPy \citep{scipy}, \textsc{matplotlib} \citep{Hunter:2007}, \textsc{Astropy} \citep{2013A&A...558A..33A}, \textsc{NumPy} \citep{van2011numpy}, \textsc{isochrones} \citep{isochrones}, \textsc{Julia} \citep{Bezanson2017}.}
